Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-25 paper/paper.tex
another little rework of the canon s5 para

Requirement 4 had the greatest effect on our design decision. Typically, only high-end SLR-type still cameras provide a socket for remote control. These are beyond our price range, and are much larger and heavier than we would like.
We built a prototype using a Canon Powershot S5 IS \cite{powershotS5}, a camera which has no electrical remote control input, by soldering wires to the push-button pads for the shutter and zoom buttons. Those wires were attached to isolating transistors, and a microcontroller was used to control the buttons remotely But after some time, this clever circumvention accidentally burned out the whole camera, and we abandoned the scheme.

>>>>

Requirement 4 had the greatest effect on our design decision. Typically, only high-end SLR-type still cameras provide a socket for remote control. These are beyond our price range, and are much larger and heavier than we would like.

We built a prototype using a Canon Powershot S5 IS \cite{powershotS5}, a camera which has no electrical remote control input. We soldered wires to the push-button pads for the shutter and zoom buttons so we could override them remotely. Those wires were attached to isolating transistors, and a microcontroller was used for control. After some time, this clever circumvention of the factory anti-static shielding resulted in a burnt out camera. We abandoned this scheme.
